### 2018-10-08 Sections/essay_to_the_future_QKD.tex
sectioning

\section{The future of QKD}
% 
Quantum key distribution (QKD) is the first quantum information task
to reach commercialization. Its purpose is to distribute a secret
key between two trusted parties who share a quantum channel,
as well as a classical channel for authentication. Unlike the current
cryptography system which is based on the limit of computational power of an adversary, the security of QKD only assume the laws of physics, and a 
correct implementation.

@@

\section{Performance}
Some of the criteria for assessing the performance of a QKD scheme include key rate, distance, cost and robustness.
% 
\subsection{Key rate}
Currently, a strong disparity exists between classical and quantum key distribution rates. Classical optical communication delivers in the order of 100 Gbits per second per wavelength, whereas Mbit/s rates are achieved with QKD.
% 
 The obtained key rate depends on the performance of the detector used. For QKD based on single-photon detection techniques, to achieve a high bit rate, one requires true single-photon states, in combination with detectors with high efficiency and short dead time. The current developments are promising, with a reported quantum efficiency of $93\%$ at telecom wavelengths \cite{marsili2013detecting}.
% 
 For continuous-variable QKD systems, increasing the bandwidth of the homodyne/heterodyne detectors whilst keeping the electronic noise low is essential.

\subsection{Distance}
Extending the range of QKD systems is a major challenge and driving factor for QKD in terms of future network applications. Basically, two approaches are being pursued -- free space and repeaters.  A quantum repeater, similar
to its classical analogue, is a device that can extend the range of quantum communication between sender and receiver. However, one cannot amplify the signal that contains the quantum information, which we know based on the no-cloning theorem. The no-cloning theorem states that one cannot make copies of an unknown quantum state whilst leaving the original one unchanged, which is the basis of the security of QKD.

@@

\subsection{Cost and robustness}
For QKD systems to be consumer-friendly, low cost and robustness are crucial features. Preferably QKD systems should make use of existing data fibre-optic infrastructure since the use of dark fibres are not only expensive, but often unavailable\cite{diamanti2016practical}. Single-photon detectors at room temperatures are also desirable, 
because this can remove the requirement for cryogenic cooling, hence reduces power consumption.

@@

\section{New protocols}
In parallel to hardware development, research effort is directed at finding new QKD protocols which can out-perform the existing ones. Two of these are high-dimensional (HD) QKD and the Round-Robin differential phase shift protocol (RR-DPS).

@@

\section{Challenge in security}
Although QKD protocols can be proven to be secure from an information-theoretic perspective, physical implementations often contain imperfections which are not considered in the model. Attacks can be designed to exploit such imperfections, on either the source or the detectors.
% 
Table ~\ref{attacks} (From Ref.~\cite{lo2014secure}) summarises some attacks against certain commercial and research systems.

@@

\subsection{QKD with imperfect sources}

The source is typically less vulnerable to attacks because Alice can prepare her quantum states in
a protected environment, and we expect that she can characterize her source. Therefore flaws in the state preparation can be incorporated into the security proof.

@@

\subsection{MID-QKD}

@@

Another candidate such as 
detector-device-independent\cite{lim2014detector,PhysRevA.92.022337} (DDI) QKD has been designed to take advantage of both the strong security of MDI-QKD, with the efficiency of conventional QKD. However, DDI-QKD has been shown to be vulnerable to attacks \cite{PhysRevLett.117.250505}.

The MID-QKD protocol has been extended to the continuous variable (CV) framework. However, this system requires homodyne detectors with efficiency $> 85\%$, and a reliable phase reference between Alice and Bob.

\section{Conclusion}

@@

\bibliography{reference}

>>>>

\section{The future of quantum key distribution}
% 
Quantum key distribution (QKD) is the first quantum information task
to reach commercialization. Its purpose is to distribute a secret
key between two trusted parties who share a quantum channel,
as well as a classical channel for authentication. Unlike the current
cryptography system which is based on the limit of computational power of an adversary, the security of QKD only assume the laws of physics, and a 
correct implementation.

@@

\subsection{Performance}
Some of the criteria for assessing the performance of a QKD scheme include key rate, distance, cost and robustness.
%

Keyrate - currently, a strong disparity exists between classical and quantum key distribution rates. Classical optical communication delivers in the order of 100 Gbits per second per wavelength, whereas Mbit/s rates are achieved with QKD.
% 
 The obtained key rate depends on the performance of the detector used. For QKD based on single-photon detection techniques, to achieve a high bit rate, one requires true single-photon states, in combination with detectors with high efficiency and short dead time. The current developments are promising, with a reported quantum efficiency of $93\%$ at telecom wavelengths \cite{marsili2013detecting}.
% 
 For continuous-variable QKD systems, increasing the bandwidth of the homodyne/heterodyne detectors whilst keeping the electronic noise low is essential.

Distance-extending the range of QKD systems is a major challenge and driving factor for QKD in terms of future network applications. Basically, two approaches are being pursued -- free space and repeaters.  A quantum repeater, similar
to its classical analogue, is a device that can extend the range of quantum communication between sender and receiver. However, one cannot amplify the signal that contains the quantum information, which we know based on the no-cloning theorem. The no-cloning theorem states that one cannot make copies of an unknown quantum state whilst leaving the original one unchanged, which is the basis of the security of QKD.

@@

Cost and robustness - 
For QKD systems to be consumer-friendly, low cost and robustness are crucial features. Preferably QKD systems should make use of existing data fibre-optic infrastructure since the use of dark fibres are not only expensive, but often unavailable\cite{diamanti2016practical}. Single-photon detectors at room temperatures are also desirable, 
because this can remove the requirement for cryogenic cooling, hence reduces power consumption.

@@

\subsection{New protocols}
In parallel to hardware development, research effort is directed at finding new QKD protocols which can out-perform the existing ones. Two of these are high-dimensional (HD) QKD and the Round-Robin differential phase shift protocol (RR-DPS).

@@

\subsection{Challenge in security}
Although QKD protocols can be proven to be secure from an information-theoretic perspective, physical implementations often contain imperfections which are not considered in the model. Attacks can be designed to exploit such imperfections, on either the source or the detectors.
% 
Table ~\ref{attacks} (From Ref.~\cite{lo2014secure}) summarises some attacks against certain commercial and research systems.

@@

QKD with imperfect sources-
the source is typically less vulnerable to attacks because Alice can prepare her quantum states in
a protected environment, and we expect that she can characterize her source. Therefore flaws in the state preparation can be incorporated into the security proof.

@@

Measurement-device-independent QKD -

@@

Another candidate such as 
detector-device-independent\cite{lim2014detector,PhysRevA.92.022337} QKD has been designed to take advantage of both the strong security of MDI-QKD, with the efficiency of conventional QKD. However, DDI-QKD has been shown to be vulnerable to attacks \cite{PhysRevLett.117.250505}.

The MDI-QKD protocol has been extended to the continuous variable framework. However, this system requires homodyne detectors with efficiency $> 85\%$, and a reliable phase reference between Alice and Bob.

@@
